Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*

### 2019-01-14 analyses/reproduce_analyses.Rmd
move all code relating to selection on extended phenotype of egg parasitoid to the end of the manuscript.
remove echo=F calls so all underlying code is displayed.

```{r Univariate_histograms, echo=FALSE, fig.cap="\\label{fig:Univariate_histograms}Histograms of each phenotypic trait after transformation. The red line illustrates a normal distribution."}
mvn_univariate_hist <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), univariatePlot = "histogram")
```

```{r Multivariate_QQ, echo=FALSE, fig.cap="\\label{fig:Multivariate_QQ}Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")
```

@@

```{r Table of food web selection gradients, echo=F}
knitr::kable(tidy_foodweb_grads)
```

@@

```{r Egg vs. larval selection gradients, echo=F}
knitr::kable(tidy_egglarval_grads)
```

@@

```{r Plot egg vs. larval ptoid gradients, echo=FALSE}

@@

```{r Figure-Selection-Gradients, echo=FALSE, fig.cap="**Selection gradients**. Estimates of standardized selection gradients in complex (orange) and simple (blue) food webs. The contribution of larval parasitoids (yellow) was estimated with a subset of the complex food-web data that only contained attacks from larval parasitoids (and gall survival). Points and lines correspond to estimates of the mean and 95% confidence intervals, respectively. Overlapping confidence intervals with zero (dotted line) indicate no strong evidence of selection.", include=FALSE}
tidy_foodwebegglarval_grads <- bind_rows(
  tidy_foodweb_grads, mutate(filter(tidy_egglarval_grads, type=="Complex"), type="Larval")
)
tidy_foodwebegglarval_grads$type <- factor(tidy_foodwebegglarval_grads$type, levels=c("Complex","Simple","Larval","Diff"))

@@

```{r Plot foodwebegglarval coefficients, echo=FALSE, fig.cap="**Partitioning Selection Gradients.**", include=FALSE}
tidy_foodwebegglarval_alphas <- bind_rows(
  tidy_foodweb_alphas, mutate(filter(tidy_egglarval_alphas, type=="Complex"), type="Larval")
)
tidy_foodwebegglarval_alphas$type <- factor(tidy_foodwebegglarval_alphas$type, levels=c("Complex","Simple","Larval","Diff"))

@@

```{r Egg vs. egg ptoid coefficients, echo=F}
knitr::kable(tidy_eggegg_alphas)
```

```{r Plot egg vs. egg ptoid coefficients, echo=FALSE}

```{r Table of egg vs. egg ptoid gradients, echo=F}
knitr::kable(tidy_eggegg_grads)
```

```{r Plot egg vs. egg ptoid gradients, echo=FALSE}

@@

```{r Univariate-Fitness-Landscapes, echo=FALSE, fig.cap="Selection gradients acting on gall traits in complex vs. simple food webs. Each panel corresponds to a different gall trait: gall diameter (A); clutch size (B); and Oviposition preference (C). Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs. Transparent lines represent bootstrapped replicates (n=100) to show the uncertainty in estimated gradients. Note that only 100 bootstraps are displayed here, but that inferences are based on 1,000 bootstrapped samples."}

@@

>>>>

```{r Univariate_histograms, fig.cap="\\label{fig:Univariate_histograms}Histograms of each phenotypic trait after transformation. The red line illustrates a normal distribution."}
mvn_univariate_hist <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), univariatePlot = "histogram")
```

```{r Multivariate_QQ, fig.cap="\\label{fig:Multivariate_QQ}Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")
```

@@

```{r Table of food web selection gradients}
knitr::kable(tidy_foodweb_grads)
```

@@

```{r Egg vs. larval selection gradients}
knitr::kable(tidy_egglarval_grads)
```

@@

```{r Plot egg vs. larval ptoid gradients}

@@

```{r Figure-Selection-Gradients, fig.cap="**Selection gradients**. Estimates of standardized selection gradients in complex (orange) and simple (blue) food webs. The contribution of larval parasitoids (yellow) was estimated with a subset of the complex food-web data that only contained attacks from larval parasitoids (and gall survival). Points and lines correspond to estimates of the mean and 95% confidence intervals, respectively. Overlapping confidence intervals with zero (dotted line) indicate no strong evidence of selection.", include=FALSE}
tidy_foodwebegglarval_grads <- bind_rows(
  tidy_foodweb_grads, mutate(filter(tidy_egglarval_grads, type=="Complex"), type="Larval")
)
tidy_foodwebegglarval_grads$type <- factor(tidy_foodwebegglarval_grads$type, levels=c("Complex","Simple","Larval","Diff"))

@@

```{r Plot foodwebegglarval coefficients, fig.cap="**Partitioning Selection Gradients.**", include=FALSE}
tidy_foodwebegglarval_alphas <- bind_rows(
  tidy_foodweb_alphas, mutate(filter(tidy_egglarval_alphas, type=="Complex"), type="Larval")
)
tidy_foodwebegglarval_alphas$type <- factor(tidy_foodwebegglarval_alphas$type, levels=c("Complex","Simple","Larval","Diff"))

@@

@@

```{r Univariate-Fitness-Landscapes, fig.cap="Selection gradients acting on gall traits in complex vs. simple food webs. Each panel corresponds to a different gall trait: gall diameter (A); clutch size (B); and Oviposition preference (C). Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs. Transparent lines represent bootstrapped replicates (n=100) to show the uncertainty in estimated gradients. Note that only 100 bootstraps are displayed here, but that inferences are based on 1,000 bootstrapped samples."}

@@

```{r Egg vs. egg ptoid coefficients}
knitr::kable(tidy_eggegg_alphas)
```

```{r Plot egg vs. egg ptoid coefficients}

```{r Table of egg vs. egg ptoid gradients}
knitr::kable(tidy_eggegg_grads)
```

```{r Plot egg vs. egg ptoid gradients}
